Stochastic Variance-Reduced Policy Gradient

### 2018-06-26 poster/poster.tex
Updated

\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
\documentclass[landscape,a0paper,fontscale=0.312]{baposter}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Motivation}{name=motiv,column=0,row=0,span=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\noindent We want to solve \textbf{continuous} Markov Decision Processes (MDPs), \eg robot locomotion

@@

	\noindent\textbf{Policy Gradient} (PG): optimize a parametric policy $\pi_{\vtheta}$ via \textbf{gradient ascent} on performance $J(\vtheta)$.

@@

	\noindent Two main strategies for gradient computation:

	\begin{itemize}
	\item \textbf{Full Gradient (FG)}: \bad{sample infefficient} \\$\longrightarrow O(\nicefrac{N}{\epsilon})$
	\item \textbf{Stochastic Gradient (SG)}: \bad{slow convergence} \\$\longrightarrow O(\nicefrac{1}{\epsilon^2})$
	\end{itemize}

	\noindent Sample efficiency is crucial in Reinforcement Learning (RL), where collecting samples is extremely expensive $\implies$ \textbf{FG} often unfeasible.

	\noindent Slower convergence of \textbf{SG} due to \bad{gradient variance}.
	\\A solution from the Supervised Learning (SL) literature (finite-sum optimization):
	\begin{itemize}
		\item \textbf{Stochastic Variance-Reduced Gradient (SVRG)} $\longrightarrow O(N+\nicefrac{N^{\nicefrac{2}{3}}}{\epsilon})$
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Problem}{name=problem,column=0,row=1, span=1,below=motiv}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\noindent Can we apply \textbf{SVRG} to policy optimization?\\
	Compared to SL, RL has three additional challenges:
	\begin{enumerate}
		\item \chall{Non-concavity}: policy performance $J(\vtheta)$ is typically a non-concave objective
		\item \chall{Infinite dataset}: expectation over all possible trajectories cannot be expressed as a finite sum  
		\item \chall{Non-stationarity}: the data-generating distribution changes as we learn
	\end{enumerate}
}

\headerbox{Related Work}{name=related,column=0,row=1, span=1,below=problem,above=bottom}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\noindent From the \textbf{SL} literature, \textit{separate} study of: 
	\begin{itemize}
		\item \chall{Non-concavity}~\citep{du2017svrgpe,reddi2016stochastic}
		\item \chall{Infinite dataset}~\citep{harikandeh2015stopwasting,bietti2017stochastic}
	\end{itemize}

	\noindent From the \textbf{RL} literature:
	\begin{itemize}
		\item \textbf{SVRPGE}~\citep{du2017svrgpe}: SVRG for policy \textit{evaluation}
		\item \textbf{SVRPO}~\cite{xu2017svrgtrpo}: direct application of SVRG to TRPO
	\end{itemize}

\chall{Nonstationarity} never addressed explicitly!
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Contributions}{name=contrib,column=1,row=0, span=2}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{itemize}
		\item We design \enhance{SVRPG}, a variant of SVRG for the PG framework that explicitly addresses the \chall{challenges} of RL.
		\item We study the \textbf{convergence} properties of SVRPG
		\item  We devise \textbf{heuristics} for meta-parameter selection in order to develop a practical algorithm.
		\item We evaluate SVRPG on simulated \textbf{continuous control tasks}. 
	\end{itemize}
}

>>>>

\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
\documentclass[landscape,a0paper,fontscale=0.32]{baposter}

@@

\colorlet{redp}{red!20} % vert S
\colorlet{greenp}{vert3!20} % vert S\usepackage[framemethod=tikz]{mdframed}
\colorlet{bluep}{blue!20} % vert S
\colorlet{blueg}{blue!70!green!90!white}

\newcommand{\hl}[3][\fboxsep1pt]{{#1\colorbox{#2}{#3}}}%
%\newcommand{\hl}[2]{{\adjustbox{bgcolor=#1}{#2}}}%

\newcommand{\hlr}[1]{\hl{redp}{#1}}
\newcommand{\hlg}[1]{\hl{greenp}{#1}}
\newcommand{\hlb}[1]{\hl{bluep}{#1}}
\newcommand{\hlo}[1]{\hl{orange!50}{#1}}
\newcommand{\hly}[1]{\hl{yellow!70!black!50!white}{#1}}
\newcommand{\hlblg}[1]{\hl{blue!75!green!20!white}{#1}}
\newcommand{\tikzhlblg}[1]{\tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=blue!75!green!20!white]{{#1}};}}
\newcommand{\tikzhly}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=yellow!70!black!50!white]{{#1}};}}
\newcommand{\tikzhlr}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=redp]{{#1}};}}
\newcommand{\tikzhlg}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=greenp]{{#1}};}}
\newcommand{\tikzhlb}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=bluep]{{#1}};}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Motivation}{name=motiv,column=0,row=0,span=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
          \noindent $\blacktriangleright$~We want to solve \hlb{continuous} Markov Decision Processes (\hlb{MDPs}), \eg robot locomotion

@@

    \noindent $\blacktriangleright$~\hlg{\textbf{Policy Gradient} (PG)}: optimize a parametric policy $\pi_{\vtheta}$ via \textbf{gradient ascent} on performance $J(\vtheta)$.

@@

	\noindent $\blacktriangleright$~Two main strategies for gradient computation:

	\begin{itemize}\compresslist
	\item \textbf{Full Gradient (FG)}: \bad{sample infefficient} \\$\longrightarrow O(\nicefrac{N}{\epsilon})$
	\item \textbf{Stochastic Gradient (SG)}: \bad{slow convergence} \\$\longrightarrow O(\nicefrac{1}{\epsilon^2})$
	\end{itemize}

    \begin{minipage}{.85\textwidth}
    \noindent \hly{Sample efficiency} is crucial in Reinforcement Learning (RL), where collecting samples is extremely expensive\\ 
    \hspace*{.3cm} $\implies$ \textbf{FG} often \underline{unfeasible}

	\vspace{2mm}
	\noindent Slower convergence of \textbf{SG} due to high \hly{gradient variance}.
    \end{minipage}

    \vspace{.3cm}
    \noindent $\blacktriangleright$~ \hlr{Solution:} from finite-sum optimization in Supervise Learning:
	\begin{itemize}\compresslist
		\item \textbf{Stochastic Variance-Reduced Gradient (SVRG)} $\longrightarrow O(N+\nicefrac{N^{\nicefrac{2}{3}}}{\epsilon})$
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{SVRG in RL: challenges}{name=problem,column=0,row=1, span=1,below=motiv}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	\noindent Can we apply \textbf{SVRG} to policy optimization?\\
        \noindent \hlb{\textbf{Goal:}} replace SG in RL with SVRG\\[.1cm]
        \hspace*{2cm}\underline{RL introduces three challenges}
%	Compared to SL, RL has three additional challenges:
	\begin{enumerate}
		\item \chall{Non-concavity}: policy performance $J(\vtheta)$ is typically a non-concave objective
		\item \chall{Infinite dataset}: expectation over all possible trajectories cannot be expressed as a finite sum  
        \item \chall{Non-stationarity}: the data-generating distribution changes as we learn (policy changes)
	\end{enumerate}
}

\headerbox{What is out there?}{name=related,column=0,row=1, span=1,below=problem,above=bottom}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \noindent From the \hlb{\textbf{SL}} literature, \textit{separate} study of: 
	\begin{itemize}\compresslist
		\item \chall{Non-concavity}~\citep{du2017svrgpe,reddi2016stochastic}
		\item \chall{Infinite dataset}~\citep{harikandeh2015stopwasting,bietti2017stochastic}
	\end{itemize}

    \noindent From the \hlb{\textbf{RL}} literature:
	\begin{itemize}\compresslist
		\item \textbf{SVRPGE}~\citep{du2017svrgpe}: SVRG for policy \textit{evaluation}
		\item \textbf{SVRPO}~\citep{xu2017svrgtrpo}: direct application of SVRG to TRPO
	\end{itemize}

\chall{Non-stationarity} never addressed explicitly!
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Contributions}{name=contrib,column=1,row=0, span=2}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        {\color{red} Questa possiamo magari toglierla}
	\begin{itemize}
		\item We design \enhance{SVRPG}, a variant of SVRG for the PG framework that explicitly addresses the \chall{challenges} of RL.
		\item We study the \textbf{convergence} properties of SVRPG
		\item  We devise \textbf{heuristics} for meta-parameter selection in order to develop a practical algorithm.
		\item We evaluate SVRPG on simulated \textbf{continuous control tasks}. 
	\end{itemize}
}
